Joint Neighborhood Subgraphs Link Prediction

### 2017-06-30 paper.tex
F

Supervised learning link prediction methods are based on a learning process which try to learn a curve that separates present links and absent links relied on their characteristics. This group of methods can also be further grouped into four subsets: feature-based models, graph regularization models, latent class models and latent feature models as presented in \cite{matrix-factorization}. In \cite{nonparametric}, a nonparametric latent feature models for link prediction is introduced in which latent features are extracted by based on an adaptation of Bayesain nonparametric approach. Besides, this method is able to concurrently learn number of latent features and assign which entities have these features. Another method related to latent features is presented in \cite{matrix-factorization}, they propose to use matrix factorization to extract latent features. This method can also take the output of unsupervised methods as its input to proceed. They show impressive results with different use of loss functions: square loss function, log loss function. Compared to unsupervised learning methods, supervised methods tend to show better performance in general. However, they normally face with the high complexity in term of computation and memory consumption.

In this work we present a novel supervised approach based on pure topological information.

@@

>>>>

Supervised link prediction methods convert the problem into a binary classification task where links present in the network (at a given time) are considered as positive instances and a subset of all the non links are considered as negative instances. Following \cite{matrix-factorization}, we can further group these methods into four classes: feature-based models, graph regularization models, latent class models and latent feature models. 
A Bayesian nonparametric approach is used in \cite{nonparametric} to compute a nonparametric latent feature model that does not need a user defined number of latent features but rather induces it as part of the training phase. 
In \cite{matrix-factorization} a matrix factorization approach is used to extract latent features that can take into consideration the output of an unsupervised method. The authors show impressive increase in predictive performance when considering a ranking loss function to deal with the imbalance problem (i.e. a much larger number of negative vs positive instances).

In general supervised methods exhibit better accuracies compared to unsupervised methods although incurring in much higher computational and memory complexity costs.

@@

In this work we present a novel supervised approach based on pure topological information.
The main contribution is
